\documentclass{note}

\usepackage{geometry}
\usepackage{stmaryrd}
\usepackage{xifthen}
\usepackage{tikz-cd}

\newcounter{exercise}[section]
\newcommand{\Ex}{%
    \stepcounter{exercise}% Increment the counter
    \subsubsection*{\thesection.\arabic{exercise}.}% Print the section title
}

\newcommand{\Affine}[2][]{\mathbf{A}^{#2}\ifthenelse{\isempty{#1}}{}{_{#1}}}
\newcommand{\Proj}[1]{\mathbf{P}^{#1}}
\newcommand{\lring}[2][]{\mathcal{O}_{#2\ifthenelse{\isempty{#1}}{}{,#1}}}

\newcommand{\id}{\mathrm{id}}
\newcommand{\union}{\cup}
\newcommand{\closure}{\overline}
\newcommand{\cmpl}[1]{#1^\text{c}}
\newcommand{\chevrons}[1]{\left\langle#1\right\rangle}
\newcommand{\rational}[2]{\chevrons{#1,#2}}
\newcommand{\divides}{\mid}
\newcommand{\ndivide}{\nmid}

\renewcommand{\theenumi}{\alph{enumi}}

\begin{document}

\chapter{Varieties}

\section{Affine Varieties}

\Page{3}

\Topic{Example 1.1.4.}

The converse statement is also true, so we have
\begin{proposition*}
  Let $Y$ be a subset of $X$. $Y$ is irreducible if and only if its closure
  $\closure{Y}$ is irreducible.
\end{proposition*}
\begin{proof}
  Assume $Y$ is irreducible, we show $\closure{Y}$ is also irreducible. Assume
  $\closure{Y} \subseteq Y_1 \cup Y_2$ where $Y_1$ and $Y_2$ are closed in $X$
  and $\closure{Y} \nsubseteq Y_1$. Then $Y \subseteq Y_1 \cup Y_2$ and $Y
    \nsubseteq Y_1$ (otherwise $\closure{Y} \subseteq Y_1$), which together with
  $Y$ being irreducible implies $Y \subseteq Y_2$, thus $\closure{Y} \subseteq
    Y_2$.

  Conversely, let $\closure{Y}$ be irreducible, we show $Y$ is also irreducible.
  Assume $Y \subseteq Y_1 \cup Y_2$ where $Y_1$ and $Y_2$ are closed in $X$ and
  $Y \nsubseteq Y_1$. Then $\closure{Y} \subseteq Y_1 \cup Y_2$ (because $Y_1
    \cup Y_2$ is closed) and obviously $\closure{Y} \nsubseteq Y_1$, so
  $\closure{Y} \subseteq Y_2$, implying $Y \subseteq Y_2$.
\end{proof}

\Page{4}

\Topic{Corollary 1.4.}

We have a more general result about whether any subset of $\Affine{n}$ is
irreducible.
\begin{proposition*}
  A subset $Y$ of $\Affine{n}$ is irreducible if and only if $I(Y)$ is a prime
  ideal.
\end{proposition*}
\begin{proof}
  Assume $Y$ is irreducible. $\closure{Y}$ is also irreducible according to the
  proposition above. By Proposition 1.2.(e) in the book, one has $Z(I(Y)) =
    \closure{Y}$ is irreducible. Now if we show $I(Y)$ is radical, it then follows
  from Corollary 1.4 that under the inclusion-reversing correspondence, $I(Y)$ is
  prime. Recall that $I(Y) = \setbuilder{f \in
      \polynomials{k}{x_1}{\dots}{x_n}}{f(P) = 0\text{ for all }P \in Y}$. Now if
  $f^r \in I(Y)$, then for all $P \in Y$, $f^r(P) = 0$, thus $f(P) = 0$.

  Conversely, suppose $I(Y)$ is prime. Using Proposition 1.2.(e) again, we have
  $\closure{Y} = Z(I(Y))$. It then follows from Corollary 1.4 that $\closure{Y}$
  is irreducible, and so is $Y$ by the proposition above.
\end{proof}

\Page{7}

\Topic{Exercises}

\setcounter{exercise}{1}

\Ex

$Y$ is the zero set of the ideal $(x^2-y,x^3-z)$. One only needs to show
that $A(Y)$ is isomorphic to a polynomial ring in one variable, from which the
rest follows.

\setcounter{exercise}{11}

\Ex

For one example, $f = x^2 + y^2 + 1$ is irreducible in
$\polynomials{\reals}{x}{y}$ (can be proved by assuming factors of $f$, viewing
them as polynomials in $\polynomials{\polynomials{\reals}{x}}{y}$), but $Z(f)$
in $\Affine[\reals]{2}$ is $\emptyset$ and not considered to be irreducible by
definition of irreducible sets.

For another example, $f = x^2(x-1)^2 + y^2$ is irreducible in
$\polynomials{\reals}{x}{y}$ (the unique factorization of $f$ in
$\polynomials{\complexes}{x}{y}$ is $(x(x-1) + iy)(x(x-1) - iy)$, but none of
the two factors is in $\polynomials{\reals}{x}{y}$), but $Z(f) = \set{(0,
    0)}{(1, 0)}$ is not irreducible.

\section{Projective Varieties}
\Page{13}

\Topic{Exercises}

\setcounter{exercise}{11}

\Ex
\begin{enumerate}
  \item Since polynomial rings are integral, so is
        $\polynomials{k}{y_0}{\dots}{y_N}/\ideal{a}$, so $\ideal{a}$ is prime. (Need to
        show it is homogeneous?)
  \item $\rho_d(\Proj{n})\subset Z(\ideal{a})$ is
        obvious. In fact for any $\rho_d(P)=(M_0(a),\dots,M_N(a))$, and any
        $f\in\ideal{a}$, we have $f(\rho_d(P)) = f(M_0(a),\dots,M_N(a))
          \xlongequal{\text{by definition of }\theta} \theta(f)(a) = 0.$\\
        $Z(\ideal{a})\subset\rho_d(\Proj{n})$ is trivial. Just need to construct
        $\rho_d^{-1}(P)$ from $P\in Z(\alpha)$.
  \item One direction is easy. To show $\rho_d^{-1}$ is continuous, one needs to look
        at the open sets $U_i$.
\end{enumerate}

\section{Morphisms}

\Page{20}

\Topic{Exercises}

\Ex
\begin{enumerate}
  \item
  \item
  \item Any non-degenerate linear transformation $\mathbf{x} \mapsfrom M\mathbf{x}$
        induces an isomorphism between a variety and its image. For any conic $Ax^2 +
          By^2 + Cz^2 + Dyz + Ezx + Fxy = 0$ in $\Proj{2}$, we show under a suitable
        transformation it becomes $xy = z^2$.
        \begin{itemize}
          \item If at most one in $A$, $B$, $C$ is nonzero, say $C$, dehomogenize with respect
                to $z$ we get
                \begin{equation*}
                  Fxy + Ex + Dy + C = 0.
                \end{equation*}
                Obviously $F \ne 0$ and by change of variables we can bring it to
                \begin{equation*}
                  xy = 1.
                \end{equation*}
                That the constant term is not zero is a consequence of the fact that the
                quadratic equation is irreducible. Now homogenize to $z$ and we get the desired
                form.
          \item If two or more in $A$, $B$, $C$ are nonzero, say $A$ and $B$. Dehomogenize
                w.r.t.~$z$ to get
                \begin{equation*}
                  Ax^2 + Fxy + By^2 + Ex + Dy + C = 0.
                \end{equation*}
                By transformation
                \begin{equation*}
                  \begin{bmatrix}
                    x \\ y
                  \end{bmatrix}
                  \mapsfrom
                  \begin{bmatrix}
                    \sqrt{B} & \sqrt{B}  \\
                    \sqrt{A} & -\sqrt{A}

                  \end{bmatrix}
                  \begin{bmatrix}
                    x \\ y
                  \end{bmatrix}
                \end{equation*}
                the curve is brought to $(2AB + F\sqrt{AB})x^2 + (2AB - F\sqrt{AB})y^2 + E'x +
                  D'y + C = 0$. Since $A,B\ne0$, divide by $\sqrt{AB}$ to get $(2\sqrt{AB} +
                  F)x^2 + (2\sqrt{AB} - F)y^2 + E'x + D'y + C' = 0$. The two quadratic
                coefficients cannot be both 0, so the equation can be converted into either
                \begin{equation*}
                  x^2 + y^2 = 1, \quad \text{or} \quad x^2 = y.
                \end{equation*}
                In the second case it is already the desired form. In the first case
                homogenization gives $x^2 + y^2 = z^2$. Write $(x + iy)(x - iy) = z^2$ and we
                are done.
        \end{itemize}
        Now we need to show the curve $Y$ given by $xy = z^2$ is isomorphic to
        $\Proj{1}$. Consider the map $\varphi\colon\Proj{1} \to Y$ given by
        $\varphi((x,y)) = (x^2,y^2,xy)$. It is not hard to check that it admits an
        inverse.
  \item
  \item
\end{enumerate}

\setcounter{exercise}{2}

\Ex
\begin{enumerate}
  \item Need to varify: well-definedness, compatibility with ring structures.
  \item ``$\implies$'': Trivial.\\ ``$\impliedby$'': Only need to
        show $\varphi^{-1}$ is a morphism. For any open subset $U$ of $X$ and any
        regular function $f$ on $U$, need to show $f\circ\varphi^{-1}$ is regular on
        $\varphi(U)$. For any point $\varphi(P)$ in $\varphi(U)$, since $\varphi_P^*$
        is an isomorphism, $f$ viewed as a function in $\lring[X]{P}$ has some preimage
        $g\in\lring[Y]{\varphi(P)}$. Because $\varphi_P^*(g) = g\circ\varphi$, $f$ and
        $g\circ\varphi$ agree on some open set $V\subset U$. In other words,
        $f\circ\varphi^{-1} = g$ on $\varphi(V)$, proving $f\circ\varphi^{-1}$ is
        regular at $\varphi(P)$.
  \item Suppose $\chevrons{V,g}\in\lring[Y]{\varphi(P)}$ and $0 = \varphi_P^*(g) =
          g\circ\varphi$. Then $g\circ\varphi$ vanishes in an open neighborhood of $P$
        contained in $\varphi^{-1}(V)$, which means it vanishes in
        $\varphi^{-1}(V)\eqqcolon U$. Thus $g$ vanishes in $\varphi(U)$. Now the
        closure of $\varphi(X)$ is contained in $\closure{\varphi(U)}\union\cmpl{V}$.
        Since $\varphi(X)$ is dense in $Y$, we have $\closure{\varphi(U)}\union\cmpl{V}
          = Y$. This is the case only if $V\subset\closure{\varphi(U)}$, in which $g$
        vanishes. Thus we conclude $g = 0$ in $\lring[Y]{\varphi(P)}$.
\end{enumerate}

\setcounter{exercise}{4}

\Ex

Follow hints. More details to be added.

\setcounter{exercise}{6}

\Ex

Just prove (b).

\section{Rational Maps}
\Page{24}

\Topic{The composition of dominant rational maps is dominant}

Let $\rational{U}{\varphi_U}$ be dominant rational map from $X$ to $Y$ and
$\rational{V}{\psi_V}$ be dominant from $Y$ to $Z$. The composition is defined
where $\psi_V\circ\varphi_U$ is defined. Let $V'\coloneqq\varphi_U(U)\cap V$.
If $W\coloneqq\closure{\psi_V(V')}$ is not $Z$, then obviously $\psi_V^{-1}(W)
  \subsetneq V$, thus $\psi_V^{-1}(Z\setminus W)$ is a nonempty open subset of
$V$, thus open in $Y$. Now $\varphi_U(U) \cap \psi_V^{-1}(Z\setminus W) =
  \varnothing$ (since $\varphi_U(U) \cap V \subset V' \subset \psi_V^{-1}(W)$),
contradicting that $\varphi_U(U)$ is dense.

\Page{30}

\Topic{Exercises}

\setcounter{exercise}{3}

\Ex
\begin{enumerate}
  \item By exercise 3.1(c). \item \item
\end{enumerate}

\section{Nonsingular Varieties}
\Page{32}

\Topic{Details in the proof of theorem 5.1 about the localization properties}
\begin{proposition*}
  Let $A$ be a ring, $\ideal{b}$ an ideal, $\ideal{a} \supset \ideal{b}$ a
  maximal ideal. Let $\mathcal{O}$ be the localization of the quotient ring
  $A/\ideal{b}$ at $\ideal{a}/\ideal{b}$, and $\ideal{m}$ the maximal ideal of
  $\mathcal{O}$. Then $\ideal{m} = (\ideal{a})$. The residues fields
  $\mathcal{O}/\ideal{m}$ and $A/\ideal{a}$ are isomorphic. Denote this field by
  $k$. Then $\ideal{m}/\ideal{m}^2$ and $\ideal{a}/(\ideal{a}^2+\ideal{b})$ are
  vector spaces over $k$. We have the following isomorphism of vector spaces:
  \begin{equation*}
    \ideal{m}/\ideal{m}^2 \cong \ideal{a}/(\ideal{a}^2+\ideal{b}).
  \end{equation*}
\end{proposition*}

\begin{proof}
  We first show the isomorphism between $\mathcal{O}/\ideal{m}$ and
  $A/\ideal{a}$. Consider the ring morphism $\alpha\colon A \to
    \mathcal{O}/\ideal{m}$ defined via the natural morphism $x \mapsto
    \frac{\bar{x}}{1}+\ideal{m}$, where $\bar{x}$ denotes the equivalent class of
  $x$ in $A/\ideal{b}$. Then $\alpha$ is onto. In fact any element in
  $\mathcal{O}/\ideal{m}$ has a representative $\frac{\bar{x}}{\bar{y}}$, where
  $x\in A$, $y \in A\setminus\ideal{a}$. Since $\ideal{a}$ is maximal, $y$ has an
  inverse $\!\ilmod\ideal{a}$ and we are done. One can also show that the kernel
  of $\alpha$ is $\ideal{a}$. Therefore we obtain the isomorphism $A/\ideal{a}
    \xrightarrow{\sim} \mathcal{O}/\ideal{m}$.

  To show the two vector spaces are isomorphic we consider the linear map
  $\varphi\colon \ideal{a} \to \ideal{m}/\ideal{m}^2$ defined also by the natural
  morphism $x\mapsto\frac{\bar{x}}{1}+\ideal{m}^2$. We first show $\varphi$ is
  onto. Any element in $\ideal{m}/\ideal{m}^2$ has a representative
  $\frac{\bar{x}}{\bar{y}}$, where $x \in \ideal{a}$, $y \in
    A\setminus\ideal{a}$. Suppose $yz \equiv 1 \ilmod \ideal{a}$, then
  $\bar{y}\bar{z} \equiv 1 \ilmod \ideal{m}$, or $\frac{1}{\bar{y}}-\bar{z} \in
    \ideal{m}$. Therefore $\bar{x}\left(\frac{1}{\bar{y}}-\bar{z}\right) \in
    \ideal{m}^2$ which means $\frac{\bar{x}}{\bar{y}} \equiv \bar{x}\bar{z} \ilmod
    \ideal{m}^2$, and we get $\varphi(xz) = \bar{x}\bar{z}+\ideal{m}^2 =
    \frac{\bar{x}}{\bar{y}}+\ideal{m}^2$. We then show that the kernel of $\varphi$
  is $\ideal{a}^2+\ideal{b}$. For $x \in \ideal{a}$, $\varphi(x) = 0$ if and only
  if $\bar{x} = x+\ideal{b} \in \ideal{m}^2 = (\ideal{a}^2)$, or $x+\ideal{b} =
    \frac{h+\ideal{b}}{g+\ideal{b}}$ for some $h\in\ideal{a}^2$ and $g\in
    A\setminus\ideal{a}$. We then get $xg - h \in \ideal{b}$. There exists some $f$
  such that $fg-1\in \ideal{a}$, therefore $x = x(1-fg+fg) = x(1-fg) + xfg =
    x(1-fg) + x(fg - h) + xh \in \ideal{a}^2 + \ideal{b} + \ideal{a}^3 =
    \ideal{a}^2+\ideal{b}$.
\end{proof}

\Page{37}

\Topic{Exercises}

\setcounter{exercise}{4}

\Ex
\begin{itemize}
  \item If $p\ndivide d$ consider $x^d + y^d + z^d = 0$.
  \item If $p\divides d$ consider $x^{d-1}y + y^{d-1}z + z^{d-1}x = 0$. The polynomial
        is irreducible since $x^{d-1}y + y^{d-1} + x$ is (Eisenstein's criterion on
        integral domains). Further more it is nonsingular.
\end{itemize}

\setcounter{exercise}{7}

\Ex

Use the fact that if $g_i$ is a polynomial of degree $d$, and $f_i$ is
homogeneous polynomial
\begin{equation*}
  f_i = x_0^d g_i\left(\frac{x_1}{x_0}, \dots, \frac{x_n}{x_0}\right),
\end{equation*}
then
\begin{equation*}
  \frac{\partial f_i}{\partial x_j} = x_0^d\frac{\partial g_i}{\partial
    x_j}\frac{1}{x_0} = x_0^{d-1}\frac{\partial g_i}{\partial x_j}.
\end{equation*}

\section{Nonsingular Curves}
\Page{40}

\Topic{Every localization of a Dedekind domain at a nonzero prime ideal is a
  discrete valuation ring} Need that noetherian and dimension are also local
properties?

\Topic{Closed proper subsets of a curve are finite}

By dimension theory. See
\href{https://math.stackexchange.com/questions/140592/closed-proper-subvarieties-of-curves-are-finite-sets-of-points}
{this answer} on Stack Exchange. A similar argument can be used to show that a
variety of dimension 1 must be a single point.

\Page{44}

\Topic{The uniqueness of $\bar\varphi$ is clear by construction}

Suppose $\bar\varphi'$ is another morphism extending $\varphi$. Then
$x_i/x_k\circ\bar\varphi'$ and $x_i/x_k\circ\bar\varphi$ agree on an open
subset of $X$ (for all $i$), thus must be the same regular function on $X$. In
particular, $x_i/x_k\circ\bar\varphi'(P) = x_i/x_k\circ\bar\varphi(P) =
  f_{ik}(P)$, i.e., $\dfrac{\bar\varphi'(P)_i}{\bar\varphi'(P)_k} = f_{ik}(P)$,
showing $\bar\varphi(P) = \varphi(P)$.

\Topic{Theorem 6.9 paragraph 2: why not use lemma 6.5 to prove local
  isomorphisms.} Actually lemma 6.5 only constructs an affine nonsingular curve
with the appropriate affine coordinate ring, without proving any isomorphisms.

\Page{45}

\Topic{Theorem 6.9 last paragraph.}

A bijective map between two curves (abstract or not) is necessarily a
homeomorphism, because the closed sets of a curve are just finite sets.

\Page{46}

\Topic{Corollary 6.12}

Denote the functor (i) $\to$ (ii) $\to$ (iii) by $F$ and (iii) $\to$ (i) by
$G$. We need to show $GF=\id_{\text{(i)}}$ and $FG=\id_{\text{(iii)}}$.

For a nonsingular projective curve $X$, let $K$ be its function field. Then
$GF(X) = C_K$. One needs to construct an isomorphism $\mu_X\colon X\to C_K$.
$X$ and $C_K$ are birational since they have the same function field $K$. Thus
there exist open sets $U$ and $V$ in $X$ and $C_K$ respectively, which are
isomorphic. Let $\mu\colon U\to V$ be the isomorphism and $\nu$ be its inverse.
Since $X$ and $C_K$ are both nonsingular projective curves, by (6.8) one can
uniquely extend $\mu$ and $\nu$ to $\bar\mu\colon X\to C_K$ and $\bar\nu\colon
  C_K\to X$. Now $\bar\nu\circ\bar\mu$ is an extension of $\nu\circ\mu = \id_U$,
which on the other hand extends (uniquely) to $\id_X$. Therefore we get an
isomorphism $\bar\mu\colon X\to C_K$.

For any nonsingular projective curves $X_1$ and $X_2$ and dominant morphism
$\varphi\colon X_1\to X_2$. One needs to show the following diagram commutes.
\begin{equation*}
  \begin{tikzcd}[row sep=huge,column sep=huge]
    X_1 \arrow{r}{\mu_{X_1}} \arrow[swap]{d}{\varphi} & C_{K_1}
    \arrow{d}{GF(\varphi)} \\ X_2 \arrow{r}{\mu_{X_2}} & C_{K_2}
  \end{tikzcd}
\end{equation*}
However the same commutative diagram with rational maps in place of the
morphisms exists due to the equivalence of categories in (4.4). Then by going
to extensions we get the desired result.

\Topic{Exercises}

\Ex
\begin{enumerate}
  \item $Y$ is isomorphic to an open subset of a nonsingular projective
        curve $X$ by corollary 6.10. Then $X$ and $\Proj1$ are birational, and hence
        isomorphic due to proposition 6.8. Since $Y$ is not isomorphic to $\Proj1$ the
        result is immediate.
  \item An open set in $\Affine1$ is $\Affine1\setminus\set{x_1}{\dots}{x_n}$. It is
        isomorphic to the affine curve given by $(x-x_1)\cdots(x-x_n)y=1$ in
        $\Affine2$.
  \item Show that $A(Y)$ is isomorphic to the localization of $\polynomials{k}{x}$ at
        the polynomials $x-x_i\colon$
        \begin{equation*}
          \set{\frac{f(x)}{\prod_{i=1}^n(x-x_i)^{k_i}} \biggm\vert f(x) \in
            \polynomials{k}{x}}.
        \end{equation*}
\end{enumerate}

\Ex
\begin{enumerate}
  \item If $Y$ were to be singular at some point, then it must be that $y = 0$ and
        $3x^2-1 = 0$, which contradicts $y^2 = x^3 - x$. Since $Y$ is nonsingular every
        localization of $A$ is integrally closed, so $A$ is integrally closed.
  \item Only need to show that if $f(x) \in \polynomials{k}{x}$ vanishes on $Y$, then
        $f(x)$ is the zero polynomial. For every $x\in k$ there is some $P$ whose first
        coordinate is $x$, thus $f(x) = 0$ for every $x$ and we are done. $A$ is in the
        integral closure of $\polynomials{k}{x}$ since $y^2 + x^3 - x = 0$ in $K$. Then
        using the fact that $A$ is integrally closed we get the result. \item
\end{enumerate}
\end{document}
